Brados: Declarative, Programmable Object Storage

### 2016-05-25 paper.tex
capitalized title
opt update
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

\title{brados: declarative, programmable object storage}

@@

\subsection{Other Interfaces}

@@

The challenge of navigating the physical design space has served as the
primary source of motivation for selection of a declarative language. While
our implementation does not yet

>>>>

\title{Brados: Declarative, Programmable Object Storage}

@@

\subsection{Other Interfaces}
\label{sec:oi}

@@

{\bf Physical design.} The challenge of navigating the physical design space
has served as the primary source of motivation for selection of a declarative
language. While our implementation does not yet make optimization decisions we
can draw parallels between the challenges faced in physical design and the
large body of mature work in query planning and optimization. Consider the
simple interface reference counting interface described in
Section~\ref{sec:oi}.  The C++ interface makes a strong assumption about a
relatively small number of tags, and chooses to fully serialize and
deserialize a C++ \texttt{std::map} for every request and store the marshalled
data as an extended attribute.  As the number of tags grows the cost of false
sharing will increase to the point that selection of an index-based interface
will likely offer a performance advantage. While the monolithic version can
outperform for small sets of tags, this type of optimization decision is
precisely what can be achieved using a declarative interface definition that
hides low-level evaluation aspects such as physical design.

Other data structures.
